The shape of dark matter halos in the AURIGA simulations

### 2019-07-10 Document/paper.tex
figura 1 extendida nuevo caption

\begin{figure*}
  \centering
  \subfloat[halo 16 DM shape at small
    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_16_inner.png}} 
  \hfill
  \subfloat[halo 16 DM shape at big
    radius]{\includegraphics[width=0.5\textwidth]{./pics/MHD_Vs_DM/level4_DM_halo_16_outer.png}} 
  \hfill 
  \caption{DM density for inner/outer (left/right panel) DM halo regions.  
  Slice 20 percent of the max-min range in the "z" position of
  particles belonging to the main structure, centered at halo defined
  position (calculated with most bounded particle) }  
  \label{fig:slices}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \subfloat[DM shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_2.png}} 
  \hfill
  \subfloat[DM shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_DM_halo_24_4.png}} 
  \hfill

  \subfloat[MHD shape at small radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_2.png}} 
  \hfill
  \subfloat[MHD shape at large radius]{\includegraphics[width=0.5\textwidth]{level4_MHD_halo_24_4.png}} 
  \hfill 
  \caption{DM density in a slice with width one tenth of the virial radius.
  The black ellipses show the result of the fitting procedure. 
  Upper panels correspond to DM only simulations, lower panels to MHD simulations.
  Left panels show data at small radii, while right panels at large radii.}
\label{fig:slices}
\end{figure*}
